Top-down versus bottom-up cohesiveness in microbial community coalescence

### 2021-05-23 draft/draft_v3.tex
defined community hierarchy in coalescence.py; new plots (figures 4 and 5); need to run the final simulations for the final figures

% title, authors, affiliations
\title{Cohesiveness in microbial community coalescence}
\author[1,*]{Juan Diaz-Colunga}
\author[1,*]{Nanxi Lu}
\author[1,2,*]{Alicia Sanchez-Gorostiaga}
\author[1]{Chang-Yu Chang}
\author[1]{Helen S. Cai}
\author[3]{Joshua E. Goldford}
\author[4]{Mikhail Tikhonov}
\author[1,\Letter]{Álvaro Sánchez}
\affil[1]{Department of Ecology \& Evolutionary Biology
and
Microbial Sciences Institute,
Yale University, New Haven, CT, USA}
\affil[2]{Department of Microbial Biotechnology,
Centro Nacional de Biotecnología (CNB-CSIC), Cantoblanco, Madrid, Spain}
\affil[3]{Physics of Living Systems, Department of Physics,
Massachusetts Institute of Technology, Cambridge, MA, USA}
\affil[4]{Department of Physics,
Center for Science \& Engineering of Living Systems,
Washington University in St. Louis, St. Louis, MO, USA}

\affil[$\textrm{\Letter}$]{\normalfont To whom correspondence should be addressed: alvaro.sanchez@yale.edu}
\affil[*]{\normalfont These authors contributed equally}
\date{}

@@

Microbial communities often invade one another.
This has been observed, for instance, 
in river courses where terrestrial microbial communities mix with aquatic microorganisms
\cite{Mansour2018,Luo2020,Vass2021}
or in soil communities being invaded as a result of
tillage and outplanting \cite{Rillig2016} or by
aerially dispersed bacteria and funghi \cite{Evans2019}.
Gut microbiomes can invade external communities
through the host animal secretions \cite{Dutton2021},
and the skin microbiota is also subject to
invasions when making contact with environmental sources of microbes \cite{Vandegrift2019}.

@@

>>>>

% title, authors, affiliations
\title{Top-down versus bottom-up cohesiveness in microbial community coalescence}
\author[1,*]{Juan Diaz-Colunga}
\author[1,*]{Nanxi Lu}
\author[1,2,*]{Alicia Sanchez-Gorostiaga}
\author[1]{Chang-Yu Chang}
\author[1]{Helen S. Cai}
\author[3]{Joshua E. Goldford}
\author[4]{Mikhail Tikhonov}
\author[1,\Letter]{Álvaro Sánchez}
\affil[1]{Department of Ecology \& Evolutionary Biology
and
Microbial Sciences Institute,
Yale University, New Haven, CT, USA}
\affil[2]{Department of Microbial Biotechnology,
Centro Nacional de Biotecnología (CNB-CSIC), Cantoblanco, Madrid, Spain}
\affil[3]{Physics of Living Systems, Department of Physics,
Massachusetts Institute of Technology, Cambridge, MA, USA}
\affil[4]{Department of Physics,
Center for Science \& Engineering of Living Systems,
Washington University in St. Louis, St. Louis, MO, USA}

\affil[$\textrm{\Letter}$]{\normalfont alvaro.sanchez@yale.edu}
\affil[*]{\normalfont These authors contributed equally}
\date{}

@@

Microbial communities often invade one another.
This has been observed, for instance, 
in river courses where terrestrial microbes mix with aquatic microorganisms
\cite{Mansour2018,Luo2020,Vass2021}
or in soil communities being invaded as a result of
tillage and outplanting \cite{Rillig2016} or by
aerially dispersed bacteria and funghi \cite{Evans2019}.
Gut microbiomes can invade external communities
through the host animal secretions \cite{Dutton2021},
and the skin microbiota is also subject to
invasions when making contact with environmental sources of microbes \cite{Vandegrift2019}.

@@

\begin{figure}[!h]
\centering
\internallinenumbers
\includegraphics[width=13cm,keepaspectratio]{figs/fig4_v2.pdf}
\caption{\textbf{A minimal model of community coalescence.}
\textbf{a.} Blablabla...
\textbf{b.} Blablabla...}
\label{fig4}
\end{figure}

\begin{figure}[!h]
\centering
\internallinenumbers
\includegraphics[width=13cm,keepaspectratio]{figs/fig5.pdf}
\caption{\textbf{Community hierarchies determine coalescence outcomes.}
\textbf{a.} Blablabla...
\textbf{b.} Blablabla...
\textbf{b.} Blablabla... ($p=0.083$).}
\label{fig4}
\end{figure}
